Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-16 thirdPaper/draft/typeConeAssociahedra.tex
improper

\newtheorem*{thm:allPolytopalRealizationsNKC}{\cref{thm:allPolytopalRealizationsNKC}}
\begin{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{thm:allPolytopalRealizationsNKC}

@@

\para{Non-kissing complex}
%
Let~$\omega$ and~$\omega'$ be two undirected walks on~$\quiver$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) incident to the endpoints of~$\sigma$ but not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
See \cref{fig:kissingCrossing} for a schematic representation and \cref{fig:exmNonkissing}\,(middle) where the three walks are pairwise kissing.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
For example, the orange walk in \cref{fig:exmNonkissing}\,(middle) is self-kissing (at its self-intersection).
We say that a walk is \defn{proper} if it is not straight nor self-kissing.
We denote by~$\properWalks$ the set of all proper walks of~$\quiver$.

>>>>

\newtheorem*{thm:allPolytopalRealizationsNKC}{\cref{thm:allPolytopalRealizationsNKC}}
\begin{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any straight or self-kissing walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{thm:allPolytopalRealizationsNKC}

@@

\para{Non-kissing complex}
%
Let~$\omega$ and~$\omega'$ be two undirected walks on~$\quiver$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) incident to the endpoints of~$\sigma$ but not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
See \cref{fig:kissingCrossing} for a schematic representation and \cref{fig:exmNonkissing}\,(middle) where the three walks are pairwise kissing.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
For example, the orange walk in \cref{fig:exmNonkissing}\,(middle) is self-kissing (at its self-intersection).
We say that a walk is \defn{proper} if it is not straight nor self-kissing, and \defn{improper} otherwise.
We denote by~$\properWalks$ the set of all proper walks of~$\quiver$.
